Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-11-01 batchdedup/scheduling.tex
update formula

% The first is that the average turnaround time for a VM is the time it takes to
% backup all the VMs. The second, which is related to the first, is that a single
% round backup has the highest cost to maintain a consistent view of the virtual
% disks. We use Copy on Write (CoW) for this, and the consistent view must be
% maintained between stage 1a and stage 2b, which can have significant cost if
% the system must wait for every single VM before unlocking any of the VMs.
% Other studies have shown that as much as 8\% or even more of total capacity must be reserved for
% CoW \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
% data size, the write rate, and duration CoW is taking place. The data size
% isn't something we can change, nor the write rate, but we can minimize the
% duration that a given VM is undergoing CoW. By minimizing the backup time for
% individual VMs we also improve CoW cost. 
To evaulate our CoW cost, we assume the incoming writes point to random disk locations, 
which would incur a CoW operation over a segment if the write location fall into a dirty segment
for the first time (consequential writes to that segment will be re-directed 
to the new copy so there's no extra cost). Therefore the number of dirty segments needs to be copied represents
the CoW cost of a VM, which follows a poisson distribution (similar results are meaured from \cite{EMCIncrementalDataChanges}).

Our basic CoW cost model is:
\[
    CoW=n(1-e^{-m/n})
\]
    where
\[
    m=tw(1-d_1)c
\]

In the above model, $n$ is the number of dirty segments, $t$ is the time under
CoW protection, $w$ is the
write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
CoW), and $c$ is a constant determining how likely writes are to touch dirty
segments which haven't yet been copied vs. dirty segments which have already
been copied during the current backup. With this CoW cost model and the earlier
performance model, we can estimate the CoW cost of a given backup schedule.
Note that CoW ends in Stage 2b, so only the time up to the end of 2b counts
towards CoW. \todo{we still need to pick a value for $c$}

>>>>

% The first is that the average turnaround time for a VM is the time it takes to
% backup all the VMs. The second, which is related to the first, is that a single
% round backup has the highest cost to maintain a consistent view of the virtual
% disks. We use Copy on Write (CoW) for this, and the consistent view must be
% maintained between stage 1a and stage 2b, which can have significant cost if
% the system must wait for every single VM before unlocking any of the VMs.
% Other studies have shown that as much as 8\% or even more of total capacity must be reserved for
% CoW \cite{EMCIncrementalDataChanges}. The actual cost of CoW is a factor of the
% data size, the write rate, and duration CoW is taking place. The data size
% isn't something we can change, nor the write rate, but we can minimize the
% duration that a given VM is undergoing CoW. By minimizing the backup time for
% individual VMs we also improve CoW cost. 
To evaulate our CoW cost, we assume the incoming writes point to random disk locations, 
which would incur a CoW operation over a segment if the write location fall into a dirty segment
for the first time (consequential writes to that segment will be re-directed 
to the new copy so there's no extra cost). Therefore the number of dirty segments needs to be copied represents
the CoW cost of a VM.

Let $t$ be the time that a VM is under Cow protection, $w$ be the write rate
during that period, $n$ be the total number of segments and $d_1$ 
be the percentage of clean segments that don't need to
be protected, then the total number of dirty segments is
\[
n_d=n(1-d_1)
\]
and the total number of writes fall into dirty segments is
\[
w_d=tw(1-d_1)
\]
Then the total number of dirty segments that need to be copied is:
\[
Cost = n_d(1-e^{-w_d/n_d}) = n(1-d_1)(1-e^{-tw/n})
\]
From the above formula it is clear that decreasing CoW time $t$ will
reduce the CoW protection cost, 
the model we derive is similar to the results meaured by \cite{EMCIncrementalDataChanges}.
% Our basic CoW cost model is:
% \[
%     CoW=n(1-e^{-m/n})
% \]
%     where
% \[
%     m=tw(1-d_1)c
% \]

% In the above model, $n$ is the number of dirty segments, $t$ is the time under
% CoW protection, $w$ is the
% write rate during CoW, $d_1$ is the \% of clean data (which doesn't go under
% CoW), and $c$ is a constant determining how likely writes are to touch dirty
% segments which haven't yet been copied vs. dirty segments which have already
% been copied during the current backup. With this CoW cost model and the earlier
% performance model, we can estimate the CoW cost of a given backup schedule.
% Note that CoW ends in Stage 2b, so only the time up to the end of 2b counts
% towards CoW. \todo{we still need to pick a value for $c$}
